Investigating Predictors for American Attitudes on Justifiability of Abortion

### 2022-06-20 Final/FinalReport.qmd
visualization sizing

```{r vis-response}
#| warning: false
#| echo: false
ggplot(abortion_data, aes(x = aj)) +
  geom_histogram(binwidth = 1, aes(y=..density..), fill = "light blue") + 
  geom_density(color = "red") +
  labs(title = "Histogram of Abortion Attitudes",
       x = "Abortion Justifiability (1-Least, 10-Most)",
       caption = "Fig.1: The visual shows that the distribution of attitude toward abortion is trimodal, rather than bell-shaped. This may worsen our model's ability to fit the data.")+
  theme(plot.caption = element_text(hjust = 0.5))
```

@@

```{r eda-histograms}
#| warning: false
#| message: false
#| echo: false
h1 <- ggplot(abortion_data, aes(x = year)) +
  geom_bar(fill = "orange") + 
  labs(x = "Year of Survey")

@@

```{r eda-boxplots}
#| warning: false
#| echo: false
b1 <- ggplot(abortion_data, aes(x = year, group = year, y = aj)) +
  geom_boxplot() +
  labs(y = "Abortion Attitude", x = "Year of Survey ")

@@

```{r correlations}
#| warning: false
#| echo: false
ggpairs(abortion_data, 
  columns = c("year", "ideology", "cai", "godimportant", "respectauthority", "nationalpride"),
  columnLabels = c("YS", "PI", "CAI", "IG", 
                   "RA", "NP")) +
   theme(
    axis.text.y = element_text(size = 6),
    axis.text.x = element_text(angle = 45, size = 9),
    strip.text.y = element_text(angle = 0, hjust = 0),
    plot.caption = element_text(hjust = 0.5)
    ) +
  labs(title = "Correlation Matrix of Predictors of Interest", caption = "Fig.4: This matrix shows that the correlations between pairs of predictors are low, with the highest being 0.370.")

```
\pagebreak

@@

```{r ci}
#| echo: false
#| warning: false
df <- tidy(abortion_fit, conf.int = TRUE)
intercept <- df[1,]
PI_IG <- df[c(2,4),]
CAI <- df[3,]
YS <- df[c(5,6,7),]
RA_NP <- df[c(8,9,10),]

@@

```{r cv}
#| message: false
#| echo: false
set.seed(206)
folds <- vfold_cv(abortion_training, v = 10)

@@

```{r linearity}
#| echo: false
c1 <- ggplot(data = final_fit_aug, aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(title = "Plot of residuals v. fitted values", x = "Predicted values", y = "Residuals")

>>>>

```{r vis-response, fig.height=3.5, fig.width=6}
#| warning: false
#| echo: false
ggplot(abortion_data, aes(x = aj)) +
  geom_histogram(binwidth = 1, aes(y=..density..), fill = "light blue") + 
  geom_density(color = "red") +
  labs(title = "Histogram of Abortion Attitudes",
       x = "Abortion Justifiability (1-Least, 10-Most)",
       caption = "Fig.1: The visual shows that the distribution of attitude 
       toward abortion is trimodal, rather than bell-shaped. This may worsen 
       our model's ability to fit the data.")+
  theme(plot.caption = element_text(hjust = 0.5))
```

@@

```{r eda-histograms, fig.height=3.5, fig.width=6}
#| warning: false
#| message: false
#| echo: false
h1 <- ggplot(abortion_data, aes(x = year)) +
  geom_bar(fill = "orange") + 
  labs(x = "Year of Survey")

@@

```{r eda-boxplots, fig.height=3.5, fig.width=6}
#| warning: false
#| echo: false
b1 <- ggplot(abortion_data, aes(x = year, group = year, y = aj)) +
  geom_boxplot() +
  labs(y = "Abortion Attitude", x = "Year of Survey ")

@@

```{r correlations, fig.height=3.5, fig.width=6}
#| warning: false
#| echo: false
ggpairs(abortion_data, 
  columns = c("year", "ideology", "cai", "godimportant", 
              "respectauthority", "nationalpride"),
  columnLabels = c("YS", "PI", "CAI", "IG", 
                   "RA", "NP")) +
   theme(
    axis.text.y = element_text(size = 6),
    axis.text.x = element_text(angle = 45, size = 9),
    strip.text.y = element_text(angle = 0, hjust = 0),
    plot.caption = element_text(hjust = 0.5)
    ) +
  labs(title = "Correlation Matrix of Predictors of Interest", 
       caption = "Fig.4: This matrix shows that the correlations between 
       pairs of predictors are low, with the highest being 0.370.")

\pagebreak

@@

```{r ci, fig.height=4, fig.width=6}
#| echo: false
#| warning: false
df <- tidy(abortion_fit, conf.int = TRUE)
intercept <- df[1,]
PI_IG <- df[c(2,4),]
CAI <- df[3,]
YS <- df[c(5,6,7),]
RA_NP <- df[c(8,9,10),]

@@

```{r cv, fig.height=3.5, fig.width=6}
#| message: false
#| echo: false
set.seed(206)
folds <- vfold_cv(abortion_training, v = 10)

@@

```{r linearity, fig.height=3.5, fig.width=5}
#| echo: false
c1 <- ggplot(data = final_fit_aug, aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(title = "Plot of residuals v. fitted values", x = "Predicted values", 
       y = "Residuals")
